\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-03 paper.tex
fixed HoloLens
added nbs to kyoto vr

Our team worked directly under Kyoto VR founder and CEO Atticus Sims to develop
and test a mobile app to deliver an audio tour, incorporating various
augmented reality (AR) features to enhance the experience. Our app delivers a
tour of Kinkaku-ji, or The Temple of the Golden Pavilion, a popular tourist
destination in Kyoto. In this app, which we call ARuko, many of the AR features
were aimed at improving accessibility. These features include translating signs
and providing additional info on the physical map located at the site. Other
features were purely for spectacle, such as the ability to take an AR
``souvenir'' home by scanning the ticket to enter Kinkaku-ji.

@@

Furthermore, we foresee Editour being a useful tool outside of the app we
designed for Kyoto VR. The design of the Editour is agnostic about how the media
will be used. For an app like izi.TRAVEL, the images are displayed when the
associated audio tour is playing.

@@

Our team is satisfied with the final result of this project, as we feel we have
built a working platform that Kyoto VR will easily be able to build off of in
the future. This section contains our final thoughts on the project and future
work that could be done on it.

@@

On Monday, September 9\textsuperscript{th}, Atticus approached us about an
additional project he wanted us to tackle. He wanted us to adapt Kyoto VR's
NOxAR app to use ground plane detection. Currently, the NOxAR app is an AR app
for Microsoft Hololens that uses image targets with Vuforia. When viewing the
correct image target, the app projects a 3D model of a noh theater\footnote{A
form of Japanese theater originating in the 14th century structured around song
and slow dancing~\autocite{japanguide2018}.} performer dancing to background
music~\autocite{noxar2018}. What Atticus wanted was to have the app use ground
plane detection in order to display the noh performer so that it could be
displayed anywhere. Additionally, he wanted us to scale up the model so that
when displayed in AR, the performer would appear life-sized.

>>>>

Our team worked directly under Kyoto~VR founder and CEO Atticus Sims to develop
and test a mobile app to deliver an audio tour, incorporating various
augmented reality (AR) features to enhance the experience. Our app delivers a
tour of Kinkaku-ji, or The Temple of the Golden Pavilion, a popular tourist
destination in Kyoto. In this app, which we call ARuko, many of the AR features
were aimed at improving accessibility. These features include translating signs
and providing additional info on the physical map located at the site. Other
features were purely for spectacle, such as the ability to take an AR
``souvenir'' home by scanning the ticket to enter Kinkaku-ji.

@@

Furthermore, we foresee Editour being a useful tool outside of the app we
designed for Kyoto~VR. The design of the Editour is agnostic about how the media
will be used. For an app like izi.TRAVEL, the images are displayed when the
associated audio tour is playing.

@@

Our team is satisfied with the final result of this project, as we feel we have
built a working platform that Kyoto~VR will easily be able to build off of in
the future. This section contains our final thoughts on the project and future
work that could be done on it.

@@

On Monday, September 9\textsuperscript{th}, Atticus approached us about an
additional project he wanted us to tackle. He wanted us to adapt Kyoto~VR's
NOxAR app to use ground plane detection. Currently, the NOxAR app is an AR app
for Microsoft HoloLens that uses image targets with Vuforia. When viewing the
correct image target, the app projects a 3D model of a noh theater\footnote{A
form of Japanese theater originating in the 14th century structured around song
and slow dancing~\autocite{japanguide2018}.} performer dancing to background
music~\autocite{noxar2018}. What Atticus wanted was to have the app use ground
plane detection in order to display the noh performer so that it could be
displayed anywhere. Additionally, he wanted us to scale up the model so that
when displayed in AR, the performer would appear life-sized.
